### 2018-10-15 manuscript.rmd
minor table updates

>>>>

```{r}
cteno_color = "#F8766D"
poro_color = "#00BA38"
unresolved_color = "#6F94CD"

papers = read_tsv( "tables/papers.tsv" )
datasets = read_tsv( "tables/datasets.tsv" )
analyses = read_tsv( "tables/analyses.tsv" )

bootstrap_threshold = 90
posterior_prob_threshold = 95

analyses$Result = "Unresolved"
analyses$Result[ ( analyses$Inference == "Bayesian" ) & (analyses$support_porifera_sister >= posterior_prob_threshold) ] = "Porifera-sister"
analyses$Result[ ( analyses$Inference == "Bayesian" ) & (analyses$support_ctenophora_sister >= posterior_prob_threshold) ] = "Ctenophora-sister"
analyses$Result = factor( analyses$Result )

```
